Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-28 1_manuscript/itt-emotion.tex
Add: disc:price

  \subsection{Price range differences}\label{disc:price}

    % some big paragraph about changing the way they speak, and about expectations, nice surprise, etc. 
    % Introduce the concept of logical expectations vs feelings expectations.
    % For example expecting it to be clean: ok just as expected / what?! it's not clean?! / cigarette
    %             expecting them to be nice: Still feel happy after they were nice
    % Omotenashi comes in play here.

    % paragraph about differences in perceptions from each culture
    %

    % paragraph about things that stay the same across all prices

    %

>>>>

  \subsection{Satisfaction across different price ranges}\label{disc:price}

    In previous sections of this paper, we have mentioned the differences reflected in the results across hotel price ranges. Nevertheless, it is interesting to discuss this further. The most visible change in satisfaction factors across differently priced hotels is the change in language to describe their satisfaction of the same topics. We can know this by observing the adjective + noun pairs, and finding pairs with different adjectives for the same nouns. For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower priced hotels. In contrast, the adjectives that pair with the same nouns for more highly priced hotels are ``wonderful'' and ``excellent''. In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''. We can infer that the level of satisfaction is higher, and that it influences the way that customers write their reviews. However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''. Here we can see how expectations influence satisfaction and dissatisfaction in different ways.

    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where it is the meeting or exceeding of expectations that produces satisfaction. Therefore, the lack of meeting of expectations would cause dissatisfaction. In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations. This is true in dissatisfaction, where their expectation is higher in a more expensive hotel. As such, any lack of cleanliness or, in the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, the smell of cigarette, can lead to disappointment or outrage. However, we consistently see customers with high expectations for high class hotels react even more positively when satisfied. In the positive case, expectations appear to be exceeded in most cases, judging their reactions. We argue that these are two different kinds of interactions with expectations. We can observe logical expectations, where customers set a standard in their mind that the service must not fall below or they will be disappointed. For example, a customer being disappointed with dirty rooms or cigarette smell. In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience, but they don't measure it against any sort of standards. For example, having a nice customer service experience, or being treated hospitably by the staff at a high class hotel. Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations, and thus a higher satisfaction. This is where \textit{omotenashi} comes into play, and enhances the experience of the customers.

    Now, there are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels. For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges. In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range. In fact, it is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common. \cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and citing \cite{japan2014consumption}, shows that common products besides food and drink are electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit. There is an understanding that the objective of shopping in Japan has more to do with the quality of the items rather than their relation to the touristic attractions. Our results suggest that Western tourists are engaging more in the touristic attractions in comparison with shopping activities. Another interesting difference is that English-speaking tourists start using negative keywords about the price of the hotel only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is. In contrast, Chinese customers have this keyword as their top keyword across all price ranges. Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.

    While some aspects of satisfaction and dissatisfaction change depending on the price range the hotel is in, some other factors stay mostly constant for the customers of each culture. For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges. Satisfaction for cleanliness for both cultures stays constantly part of the top 10 keywords, with the exception of the most expensive one, where other keywords take its place in the ranking, although it is still high on the list. Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well. Transport and location, as discussed in section \ref{disc:location}, is also important for hotels of all classes and prices. While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower. This suggests that culturally the customers have a certain bias to consider some attributes more than others.
